---
name: Luis Francisco
surname: Gómez López
position: "Associate professor"
address: "Sede Campus Nueva Granada, kilómetro 2, vía Cajicá-Zipaquirá"
pronouns: he/him
phone: +57 3124541536
www: luifrancgom.github.io/
email: "luifrancgom@gmail.com"
twitter: luifrancgom
github: luifrancgom
linkedin: luifrancgom
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 170c3a 
output: vitae::hyndman
headerincludes:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(tibble)
```

# Some stuff about me

Economist and professor skilled in using $\Re$ and (\faRProject) $\pi$-thon (\faPython) for data science, including the [*tidyverse*](https://www.tidyverse.org/) package ecosystem.

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Barchelor degree in economics", "2009", "Universidad de los Andes", "Bogota, Colombia",
  "Master degree in economics", "2012", "Universidad de los Andes", "Bogota, Colombia"
) |>  
  detailed_entries(Degree, Year, Institution, Where)
```

# Experience

```{r}
tribble(
    ~Date, ~Company, ~Position, ~Desc, ~Where,
    "2011-2011", "Fundación Auxilium IPS", "Contractor", "Preparation of a proposal for a supported employment program for patients", "Bogota, Colombia",
    "2012-2012", "CAR Cundinamarca", "Contractor", "Support in economic and financial activities related to agreements with Fondo Nacional de Calamidades - Subcuenta Colombia Humanitaria", "Bogota, Colombia",
    "2012-2013", "CAR Cundinamarca", "Contractor", "Monitoring, control and updating of the activities of the Subdirectorate of sustainable environmental development", "Bogota, Colombia",
    "2014-2024", "Universidad Militar Nueva Granada", "Part-time Auxiliar, Full-time occasional auxiliar, assistant and associate professor", "Teaching introduction to economics, microeconomics, macroeconomics, economic globalization, conflict negotiation and marketing research and analytics", "Cajica & Bogota, Colombia",
    "2020", "Instituto para la Investigación Educativa y el Desarrollo Pedagógico", "Contractor", "Support in the development of the baseline of the Right to Education Index in Bogotá", "Bogota, Colombia"
) |>  
    detailed_entries(
        Position,
        Date,
        Company,
        Where,
        Desc
    )
```

# Publications

```{r}
bibliography_entries("cv_luifrancgom.bib") |> 
  arrange(desc(author$family), issued)
```

# Events

-   Encuentro Internacional de Investigadores en Administración 2019 y III Congreso Iberoamericano de Investigación sobre MIPYME (FAEDPYME). Business Analitycs con R para E-research en Administración de Empresas.

-   V Coloquio de Matemáticas Aplicadas. Universidad Militar Nueva Granada. Data Science Workflow with R: explaining the total fertility rate in countries as a case study.

# Certifications

-   Issuing authority: DataCamp

    -   Data Scientist with R Track. Issued May 2020 - No Expiration Date
    -   Tidyverse Fundamentals with R Track. Issued: May 2020 - No Expiration Date
    -   R Programmer Track. Issued Feb 2020 - No Expiration Date.

-   Issuing authority: Business Science

    -   Data Science For Business With R. Issued: Feb 2020 - No Expiration Date
    -   Business Analysis With R. Issued: Jul 2019 - No Expiration Date
    -   Python for Data Science Automation. Issued: Mar 2024 - No Expiration Date.
